Long name of the paper

### 2018-10-08 anzjs2018/sections/04_implementation.tex
Implementation info

\section{Implementing in realtime}
\label{sec:rt}

How we implement it, choice of software (Rcpp = R + C++).
R: dealing with data structures is easier, maintainability, interfacing
C++: speed

Overall structure:
- load
- fetch positions
- initialize or mutate+update
- update network
- make ETA predictions (vehicle state + network state)

Some of the key things:
- minimise copy, parallelisation using OMP
- moving as much computation ``outside'' of the main loop as possible
  (e.g., ``pre''-predict vehicle/network states so only update required)
  so ETAs are generated ASAP after retrieving data
- keeping the GTFS database up-to-date by fetching new data each morning
- distribution - a cloud database vs a single protobuf file with everything 
  (maintenance/reliability/speed/size)

>>>>

\section{Real-time implementation and preliminary results}
\label{sec:rt}

There are two components to the application:
the static GTFS~schedule and network data,
and the real-time modeling and prediction.
We chose \verb+Rcpp+ to develop our program,
giving us the advantages of an R~package for data manipulation 
(notably \verb+RSQLite+ and \verb+dplyr+)
and distribution, 
as well as the speed and memory management capabilities of \verb|C++|. 
As a result, all of the following has been implemented in the R package
\verb+transitr+, available on Github (\url{https://github.com/tmelliott/transitr}).
Here our focus is on the real-time aplication, so we are only discussing the real-time 
features of model's implementation.

The general structure of the main function is:
\begin{enumerate}
\item Load GTFS data from database
\item Indefinitely repeat when new data recieved \ldots
\begin{enumerate}
    \item Update or create new vehicle objects from new data
    \item Run particle filter on each vehicle to estimate update state
    \item Collect travel time information for each vehicle for any completed roads
    \item Update road network with any completed road segments
    \item Generate ETAs for vehicles
    \item Write ETAs to extended Google Protobuf binary file for distribution
\end{enumerate}
\end{enumerate}

The main concern is speed: 
we desire ETAs to be available as soon as possible after obtaining the data.
To do this, we use raw pointers to read-only GTFS objects,
and particles are only copied when resampling is required.
This is also why we chose to use protobuf as the output format,
since this is fast to write and distribute.
Steps 2b--e are performed in parallel, 
which in our test environment of a virtual machine with 8~cores, 
significantly speeds up computation.

As far as results, we have two categories:
implementation and faesibility,
and model performance;
we do not have any complex arrival time estimation method,
so no results for that are shown here.

% How we implement it, choice of software (Rcpp = R + C++).
% R: dealing with data structures is easier, maintainability, interfacing
% C++: speed

% Overall structure:
% - load
% - fetch positions
% - initialize or mutate+update
% - update network
% - make ETA predictions (vehicle state + network state)

% Some of the key things:
% - minimise copy, parallelisation using OMP
% - moving as much computation ``outside'' of the main loop as possible
%   (e.g., ``pre''-predict vehicle/network states so only update required)
%   so ETAs are generated ASAP after retrieving data
% - keeping the GTFS database up-to-date by fetching new data each morning
% - distribution - a cloud database vs a single protobuf file with everything 
%   (maintenance/reliability/speed/size)
